systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-06-06 paper/branches/useR2006/Poster/systemfit_poster.tex
Poster for useR! 2006: improved placement and sizes of boxes
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@671 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\documentclass[portrait,a0b,final]{a0poster}
\input{systemfit_poster_commands}

@@

% \fbox{
\begin{postercolumn}{0.49}
% Motivation
\posterbox{0.92\textwidth}{}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Motivation}}
{\standardfontsize
\begin{itemize}
\item many theoretical models consist of more than one equation\\
$\Rightarrow$ contemporaneously correlation of disturbance terms (likely)\\
$\Rightarrow$ \parbox[t]{0.95\textwidth}{\raggedright
   simultaneously estimation of all equations as 
   °Seemingly Unrelated Regression° (SUR) leads to efficient results}
\mbox{}
\item theoretically derived cross-equation parameter restrictions\\
$\Rightarrow$ simultaneous estimation of all equations required
\item endogeneity of some variables\\
$\Rightarrow$ \parbox[t]{0.95\textwidth}{\raggedright
   estimation using °Two-Stage Least Squares° (2SLS)
   or °Three-Stage Least Squares° (3SLS) required}
\end{itemize}
}}

@@

% Example
\posterbox{0.92\textwidth}{}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Example}}
{\standardfontsize
\begin{itemize}
\item from Kmenta (1986): Elements of Econometrics, p.~685
\item specification of the equation system:
   \bigskip\\
   \BUseVerbatim{specSystem}
\item estimation using method °SUR°:\\
   \BUseVerbatim{estSystem}
\item printing summary results:\\
   \BUseVerbatim{printResults}
\end{itemize}
}}

@@

% Advantages
\posterbox{0.92\textwidth}{}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Advantages of \texttt{systemfit}}}
{\standardfontsize
\begin{itemize}
\item all estimation procedures are publicly available in the source code
\item estimation algorithms can be easily modified to meet specific
requirements
\item the (advanced) user can control many estimation details generally
not available in other software packages
\item novices can safely ignore these estimation details
because they have reasonable defaults
\item reliability of \texttt{systemfit} has been demonstrated by comparing its estimation
results with results published in the literature
\end{itemize}
}}

@@

% Future
\posterbox{0.92\textwidth}{}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Plans for the Future}}
{\standardfontsize
\begin{itemize}
\item estimation with unbalanced data sets
\item estimation methods: LIML, FIML,  and GMM
\item fitting equation systems with serially correlated and
heteroscedastic disturbances
\item spatial econometric methods
\item improving the function \texttt{nlsystemfit}
to estimate systems of non-linear estimations
\end{itemize}
}}

>>>>

\documentclass[portrait,a0b]{a0poster}
\input{systemfit_poster_commands}

@@

% \fbox{
\begin{postercolumn}{0.49}
% Motivation
\posterbox{0.92\textwidth}{245mm}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Motivation}}
{\standardfontsize
\begin{itemize}
\item many theoretical models consist of more than one equation\\
$\Rightarrow$ contemporaneously correlation of disturbance terms (likely)\\
$\Rightarrow$ \parbox[t]{0.95\textwidth}{\raggedright
   simultaneously estimation of all equations as 
   °Seemingly Unrelated Regression° (SUR) leads to efficient results}
\mbox{}
\item theoretically derived cross-equation parameter restrictions\\
$\Rightarrow$ simultaneous estimation of all equations required
\item endogeneity of some variables\\
$\Rightarrow$ \parbox[t]{0.95\textwidth}{\raggedright
   estimation using °Two-Stage Least Squares° (2SLS)
   or °Three-Stage Least Squares° (3SLS) required}
\end{itemize}
}}

@@

% Example
\posterbox{0.92\textwidth}{245mm}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Example}}
{\standardfontsize
\begin{itemize}
\item from Kmenta (1986): Elements of Econometrics, p.~685
\item specification of the equation system:
   \bigskip\\
   \BUseVerbatim{specSystem}
\item estimation using method °SUR°:\\
   \BUseVerbatim{estSystem}
\item printing summary results:\\
   \BUseVerbatim{printResults}
\end{itemize}
}}

@@

% Advantages
\posterbox{0.92\textwidth}{}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Advantages of \texttt{systemfit}}}
{\standardfontsize
\begin{itemize}
\item all estimation procedures are publicly available in the source code
\item estimation algorithms can be easily modified to meet specific
requirements
\item the (advanced) user can control many estimation details generally
not available in other software packages
\item novices can safely ignore these estimation details
because they have reasonable defaults
\item reliability of \texttt{systemfit} has been demonstrated by comparing its estimation
results with results published in the literature
\end{itemize}
\vspace{4mm}
}}

@@

% Future
\posterbox{0.92\textwidth}{}{linewidth=2mm, framearc=0.1,
   linecolor=lightblue, fillstyle=gradient, gradangle=0,
   gradbegin=white, gradend=whiteblue, gradmidpoint=1.0,
   framesep=1em}{
{\boxheaderfontsize \textbf{Plans for the Future}}
{\standardfontsize
\begin{itemize}
\item estimation with unbalanced data sets
\item estimation methods: LIML, FIML,  and GMM
\item fitting equation systems with serially correlated and
heteroscedastic disturbances
\item spatial econometric methods
\item improving the function \texttt{nlsystemfit}
to estimate systems of non-linear estimations
\end{itemize}
\vspace{4mm}
}}
